---
title: "Exercises Day 2"
author: "Your name"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(car)
## be careful to load dplyr after MASS
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
# To solve some conflicts between packages:
select <- dplyr::select

```


# Exercise 1

You performed a cognitive experiment with a pre- and post-test design. Participants completed one session before language training and one session after language training, with two types of training: Forced and Voluntary. The identical set switching task was used for pre- and post-test. Within each switching task reaction times from pure blocks are compared to switch/repeat blocks, with the expectation that participants react faster in pure blocks than non-pure blocks.

a) Prepare the data set for use in a LME. Create a new 2-level variable called BlockType that compares pure trials against non-pure trial.

```{r Ex1a, include=TRUE}
load("CogTrainingData.RData")

```

b) Create a linear mixed effects model that tests whether there was a significant effect in the cognitive test performance for BlockType. Control for individual effects of Subject and Items.

```{r Ex1b, include=TRUE}

```
c) Given that there were two sessions of the cognitive test, before and after training, and there were two types of training, create a new model that accounts for all three variables. Which fixed effects are significant?


```{r Ex1c, include=TRUE}

```

d) You also have information regarding the age for each participant. Create a model that includes this covariate as a fixed effect. Did the outcome of the model change compared to 1a? What might be possible reasons for this?

```{r Ex1d, include=TRUE}


```
# Exercise 2

Verify the assumptions of LMEs for the last model involving age as a covariate

a) Is the dependant variable lineary related to the residuals?
```{r Ex2a, include=TRUE}


```
b) Test for constant variance in the residuals.
```{r Ex2b, include=TRUE}


```

c) Test for normal distributed residuals.
```{r Ex2c, include=TRUE}


```

d) Test for multicollinearity. Which effects are correlated with each other and what might be the reason?
```{r Ex2d, include=TRUE}


```