---
title: "Exercises Day 3"
author: "Your name"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(car)
## be careful to load dplyr after MASS
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
# To solve some conflicts between packages:
select <- dplyr::select

unloadNamespace("lmerTest")

```


# Exercise 1
a) Yesterday, we created two models for the cognitive training study, one with age and one without. Use the model provided below and compare its fit with and without Age as a fixed effect.
```{r Ex1a, include=TRUE}
load("CogTrainingData.RData")

Model_1 = lmer(RT ~ TrialType*Session*Group + Age + (1 | Subject) + (1 | Item), data=Cog_training_Data)

```

b) You have another variable called Gender and you would like to control for it as a random slope. To reduce the complexity of the model, you also focus only on the forced training group and create a new model for them. How would you add Gender to the new model and does its inclusion change the fit of the model?
```{r Ex1b, include=TRUE}


```

c) You created the maximal model below, but it does not converge. Try to reduce its complexity until it converges. What model do you end up with?

```{r Ex1c1, include=FALSE}
Model_5 = lmer(RT ~ TrialType*Session*Group + Age + SES + (1 + Session| Subject) + (1 + Session*Group + Age + SES| Item), data=Cog_training_Data)
summary(Model_5)
```
Running the model above takes alot of time so I recommend only running it in a seperate chunk in order to not restart it every time for this exercise.

```{r Ex1c2, include=TRUE}

```
# Exercise 2
Use lmerTest to see the output of Model 1 in exercise 1a. How did the output change what do the new values represent. Explain the output for the variables Session and Age.
```{r Ex2a, include=TRUE}

```
